---
title: "R Syntax Drills"
description: "Adaptive practice for core R syntax."
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: "www/styles.css"
runtime: shiny_prerendered
tutorial:
  id: "drillr-drills"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(shiny)

APP_CONFIG <- drillr:::drillr_runtime_config()
source("R/question_manifest.R")
source("R/assignment_storage.R")
source("R/syntax_checkers.R")

options(tutorial.storage = "none")

gradethis::gradethis_setup(
  pass.praise = FALSE,
  fail.encourage = FALSE,
  fail.hint = FALSE
)

learnr::tutorial_options(
  exercise.timelimit = 10,
  exercise.reveal_solution = FALSE
)
```

```{r logging-start, context="server-start", include=FALSE}
library(httr2)
source("R/logging.R")
register_logging_handlers(APP_CONFIG)
```

```{r identity-server, context="server", include=FALSE}
session$userData$identity <- shiny::reactiveVal(NULL)
session$userData$assignment_ids <- shiny::reactiveVal(
  stats::setNames(character(), character())
)
session$userData$logging_status <- shiny::reactiveVal(
  list(ok = NA, message = "Load your student ID to begin.")
)

clear_assignment_player <- function() {
  session$userData$assignment_ids(stats::setNames(character(), character()))
  session$sendCustomMessage("assignment:clear", list())
}

shiny::observeEvent(input$save_identity, {
  student_id <- trimws(input$student_id)
  student_name <- trimws(input$student_name)

  if (!grepl("^[A-Za-z0-9._@-]{2,100}$", student_id)) {
    clear_assignment_player()
    session$userData$logging_status(list(
      ok = FALSE,
      message = "Enter a valid student ID (2–100 letters, digits, ., _, @, or -)."
    ))
    return()
  }

  manifest <- read_question_manifest()
  assignments <- tryCatch(
    initialize_student_assignments(
      student_id = student_id,
      manifest = manifest,
      config = APP_CONFIG
    ),
    error = function(e) e
  )

  if (inherits(assignments, "error")) {
    clear_assignment_player()
    session$userData$logging_status(list(
      ok = FALSE,
      message = paste("Could not load your drills:", conditionMessage(assignments))
    ))
    return()
  }

  session$userData$identity(list(
    student_id = student_id,
    student_name = student_name
  ))
  drillr:::drillr_save_identity(student_id, student_name)
  set_active_assignment_player(session, assignments)

  post_log_event(
    session,
    "identity_saved",
    data = list(label = "identity"),
    config = APP_CONFIG
  )
})

shiny::observeEvent(input$forget_identity, {
  drillr:::drillr_forget_identity()
  session$userData$identity(NULL)
  clear_assignment_player()
  shiny::updateTextInput(session, "student_id", value = "")
  shiny::updateTextInput(session, "student_name", value = "")
  session$userData$logging_status(list(
    ok = NA,
    message = "Saved identity forgotten on this computer."
  ))
})

output$identity_status <- shiny::renderUI({
  status <- session$userData$logging_status()
  cls <- if (isTRUE(status$ok)) {
    "alert alert-success"
  } else if (identical(status$ok, FALSE)) {
    "alert alert-danger"
  } else {
    "alert alert-warning"
  }
  shiny::tags$div(class = cls, status$message)
})
```

## Before you begin

Your responses are graded immediately and recorded for your instructor. A question stays in your active drill list until you answer it correctly; it is then replaced by another question selected from your learning history.

Only your last student ID and optional name are remembered on this computer. Your exercise answers are not saved locally between tutorial sessions.

```{r identity-ui, echo=FALSE}
saved_identity <- drillr:::drillr_read_identity()
shiny::wellPanel(
  shiny::textInput(
    "student_id",
    "Student ID",
    value = saved_identity$student_id,
    placeholder = "e.g., abc123"
  ),
  shiny::textInput(
    "student_name",
    "Name (optional)",
    value = saved_identity$student_name,
    placeholder = "e.g., Ada Lovelace"
  ),
  shiny::actionButton("save_identity", "Load drills"),
  shiny::actionButton("forget_identity", "Forget saved identity"),
  shiny::br(), shiny::br(),
  shiny::uiOutput("identity_status")
)
```

## Your drills

<div id="assignment-waiting" class="alert alert-info">
Your questions will appear here after you load a valid student ID.
</div>

```{r question-pool, child="runtime_question_pool.Rmd"}
```

```{r assignment-player-script, echo=FALSE}
shiny::includeScript("www/assignment-player.js")
```
