---
title: "R Syntax Drills"
description: "Adaptive practice for core R syntax."
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: "www/styles.css"
runtime: shiny_prerendered
tutorial:
  id: "drillr-drills"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(shiny)

APP_CONFIG <- drillr:::drillr_runtime_config()
DRILLR_LAUNCH_BANK <- drillr:::drillr_runtime_bank()

source("R/syntax_checkers.R")
source("R/question_manifest.R")
source("R/assignment_storage.R")
source("R/progress.R")
source("R/logging.R")

options(tutorial.storage = "none")

gradethis::gradethis_setup(
  pass.praise = FALSE,
  fail.encourage = FALSE,
  fail.hint = FALSE
)

learnr::tutorial_options(
  exercise.timelimit = 10,
  exercise.reveal_solution = FALSE,
  exercise.checker = drillr_exercise_checker
)
```

```{r rendered-bank, context="data", include=FALSE}
DRILLR_RENDERED_BANK <- DRILLR_LAUNCH_BANK
```

```{r logging-start, context="server-start", include=FALSE}
fallback_config <- APP_CONFIG
fallback_config$manifest_path <- DRILLR_RENDERED_BANK$manifest_path
fallback_manifest <- DRILLR_RENDERED_BANK$manifest
register_logging_handlers(fallback_config, fallback_manifest)
register_progress_handlers()
```

```{r identity-server, context="server", include=FALSE}
DRILLR_SESSION_BANK <- DRILLR_RENDERED_BANK
SESSION_CONFIG <- APP_CONFIG
SESSION_CONFIG$manifest_path <- DRILLR_SESSION_BANK$manifest_path
SESSION_MANIFEST <- DRILLR_SESSION_BANK$manifest

session$userData$runtime_config <- SESSION_CONFIG
session$userData$question_manifest <- SESSION_MANIFEST
session$userData$identity <- shiny::reactiveVal(NULL)
session$userData$assignment_ids <- shiny::reactiveVal(
  stats::setNames(character(), character())
)
session$userData$logging_status <- shiny::reactiveVal(
  list(ok = NA, message = "Load your student ID to begin.")
)
session$userData$progress_rows <- shiny::reactiveVal(empty_progress_table())
session$userData$progress_as_of_utc <- shiny::reactiveVal("")
session$userData$progress_status <- shiny::reactiveVal(list(
  ok = NA,
  message = "Load your student ID, then open Your progress."
))

clear_assignment_player <- function() {
  session$userData$assignment_ids(stats::setNames(character(), character()))
  session$sendCustomMessage("assignment:clear", list())
}

shiny::observeEvent(input$save_identity, {
  student_id <- trimws(input$student_id)
  student_name <- trimws(input$student_name)

  if (!grepl("^[A-Za-z0-9._@-]{2,100}$", student_id)) {
    clear_assignment_player()
    session$userData$logging_status(list(
      ok = FALSE,
      message = "Enter a valid student ID (2–100 letters, digits, ., _, @, or -)."
    ))
    return()
  }

  flush_summary <- flush_log_outbox(
    session,
    student_id = student_id,
    config = SESSION_CONFIG,
    manifest = SESSION_MANIFEST
  )
  if (isTRUE(flush_summary$transport_failed) || isTRUE(flush_summary$blocked)) {
    clear_assignment_player()
    session$userData$logging_status(list(
      ok = FALSE,
      message = if (nzchar(flush_summary$message)) {
        flush_summary$message
      } else {
        "Could not send locally saved responses. Try loading your drills again."
      }
    ))
    return()
  }

  assignments <- tryCatch(
    initialize_student_assignments(
      student_id = student_id,
      manifest = SESSION_MANIFEST,
      config = SESSION_CONFIG
    ),
    error = function(e) e
  )

  if (inherits(assignments, "error")) {
    clear_assignment_player()
    session$userData$logging_status(list(
      ok = FALSE,
      message = paste("Could not load your drills:", conditionMessage(assignments))
    ))
    return()
  }

  session$userData$identity(list(
    student_id = student_id,
    student_name = student_name
  ))
  set_progress_state(
    session,
    ok = NA,
    message = "Open Your progress to load your current summary.",
    rows = empty_progress_table(),
    as_of_utc = ""
  )
  drillr:::drillr_save_identity(student_id, student_name)
  set_active_assignment_player(session, assignments)

  post_log_event(
    session,
    "identity_saved",
    data = list(label = "identity"),
    config = SESSION_CONFIG,
    manifest = SESSION_MANIFEST
  )

  retired <- attr(assignments, "retired_assignments")
  notices <- character()
  if (length(retired)) {
    notices <- c(
      notices,
      "A previously assigned question was unavailable or discontinued; you have been assigned a different one."
    )
  }
  if (isTRUE(flush_summary$dropped > 0L)) {
    notices <- c(
      notices,
      "A locally saved response was not retried because that item_label is no longer available in this drill."
    )
  }
  if (length(notices)) {
    set_logging_status(
      session,
      TRUE,
      paste(c("Responses are being recorded.", notices), collapse = " ")
    )
  }
})

shiny::observeEvent(input$forget_identity, {
  drillr:::drillr_forget_identity()
  session$userData$identity(NULL)
  clear_assignment_player()
  set_progress_state(
    session,
    ok = NA,
    message = "Load your student ID, then open Your progress.",
    rows = empty_progress_table(),
    as_of_utc = ""
  )
  shiny::updateTextInput(session, "student_id", value = "")
  shiny::updateTextInput(session, "student_name", value = "")
  session$userData$logging_status(list(
    ok = NA,
    message = "Saved identity forgotten on this computer."
  ))
})

shiny::observeEvent(input$refresh_progress, {
  refresh_session_progress(session)
})

output$bank_status <- shiny::renderUI({
  messages <- c(DRILLR_SESSION_BANK$warning, DRILLR_SESSION_BANK$notice)
  messages <- messages[nzchar(messages)]
  if (!length(messages)) return(NULL)

  shiny::tags$div(
    class = "alert alert-warning",
    lapply(messages, function(message) shiny::tags$p(message))
  )
})

output$identity_status <- shiny::renderUI({
  status <- session$userData$logging_status()
  cls <- if (isTRUE(status$ok)) {
    "alert alert-success"
  } else if (identical(status$ok, FALSE)) {
    "alert alert-danger"
  } else {
    "alert alert-warning"
  }
  shiny::tags$div(class = cls, status$message)
})

output$progress_status <- shiny::renderUI({
  status <- session$userData$progress_status()
  cls <- if (isTRUE(status$ok)) {
    "alert alert-success"
  } else if (identical(status$ok, FALSE)) {
    "alert alert-danger"
  } else {
    "alert alert-info"
  }
  shiny::tags$div(class = cls, status$message)
})

output$progress_table <- shiny::renderTable({
  format_progress_table(session$userData$progress_rows())
}, striped = TRUE, bordered = FALSE, spacing = "s")

output$progress_as_of <- shiny::renderText({
  as_of <- session$userData$progress_as_of_utc()
  if (!nzchar(as_of)) return("")
  paste("Scheduler estimate as of", as_of)
})
```

## Before you begin

Your responses are graded immediately and recorded for your instructor. A question stays in your active drill list until you answer it correctly; it is then replaced by another question selected from your learning history.

Only your last student ID and optional name are normally remembered on this computer. If a response cannot reach the grading service, Drillr temporarily keeps that response in a local outbox and retries it later. Exercise answers are otherwise not saved locally between tutorial sessions.

```{r bank-status, echo=FALSE}
shiny::uiOutput("bank_status")
```

```{r identity-ui, echo=FALSE}
saved_identity <- drillr:::drillr_read_identity()
shiny::wellPanel(
  shiny::textInput(
    "student_id",
    "Student ID",
    value = saved_identity$student_id,
    placeholder = "e.g., abc123"
  ),
  shiny::textInput(
    "student_name",
    "Name (optional)",
    value = saved_identity$student_name,
    placeholder = "e.g., Ada Lovelace"
  ),
  shiny::actionButton("save_identity", "Load drills"),
  shiny::actionButton("forget_identity", "Forget saved identity"),
  shiny::br(), shiny::br(),
  shiny::uiOutput("identity_status")
)
```

## Your drills

<div id="assignment-waiting" class="alert alert-info">
Your questions will appear here after you load a valid student ID.
</div>

```{r question-pool, child=DRILLR_LAUNCH_BANK$pool_path}
```

```{r assignment-player-script, echo=FALSE}
shiny::includeScript("www/assignment-player.js")
```

## Your progress

This table summarizes the same learning history Drillr uses to choose your questions. Estimated recall is a scheduling estimate, not a grade.

```{r progress-ui, echo=FALSE}
shiny::tagList(
  shiny::uiOutput("progress_status"),
  shiny::tableOutput("progress_table"),
  shiny::textOutput("progress_as_of"),
  shiny::br(),
  shiny::actionButton("refresh_progress", "Refresh progress")
)
```
